\bf An observational study of papers published in \emph{PLOS ONE} and studies posted to a trial registry.

### 2021-04-21 manuscript/asa_template/asa_template.Rmd
update figures and tex files

@@

```{r}
load('../total.records.plos.rda')
n.api = total.records[[1]] %>% filter(stage=='API') %>% pull(n) %>% sum()
n.include = total.records[[1]] %>% filter(stage=='Included in analysis') %>% pull(n) %>% sum()
perc.include = round(100*n.include/n.api)
min.perc.stats = total.records[[2]] %>% filter(percentage==min(percentage)) %>% select(volume,percentage)
max.perc.stats = total.records[[2]] %>% filter(percentage==max(percentage)) %>% select(volume,percentage)
```

```{r}
load('../wordcount.plos.rda')
n.words = wordcounts %>% summarise(med = median(words),q1=quantile(words,.25),q3=quantile(words,.75))
p.extremes = wordcounts %>% summarise(morethan500 = round(100*mean(words>500)),lessthan50=round(100*mean(words<50)))
n.extremes = wordcounts %>% summarise(morethan500 = sum(words>500),lessthan50=sum(words<50))
```

![\label{fig:plos-n}A: Search results by _PLOS ONE_ volume; B: word count per statistical methods section included in analysis (n = 111,73); C: subject classifications assigned to full-text records included in analysis](figures/plos.summary.jpg)

```{r,fig.height=12,fig.width=6,fig.asp=0.6,fig.cap='\\label{fig:plos-n}Search results by _PLOS ONE_ volume (1st row); word count per statistical methods section included in analysis (n = 111,731; 2nd row); subject classifications assigned to full-text records included in analysis (3rd row)'}

load('../stats_section_subject.classifications.rda')
stats_section_subject = mutate(stats_section_subject,
                               top3 = ifelse(subject_level_number %in% 1:3,1,0))

@@

![\label{fig:plot-10-topics}Topic clouds summarising common terms in _PLOS ONE_ statistical methods sections assuming ten clusters](figures/plos.wordclouds.jpg)

@@

```{r}
load('../plos.results.10topics.rda')

@@

>>>>

Results were examined for evidence of boilerplate text in two ways. We first reviewed the top ten results that represented the strongest matches to each cluster. To compare results within a cluster, we calculated cosine similarity score for all pairs of records; higher scores denoted a higher degree of similarity in text between a pair of records.

@@

```{r}
load('../../results/total.records.plos.rda')
n.api = total.records[[1]] %>% filter(stage=='API') %>% pull(n) %>% sum()
n.include = total.records[[1]] %>% filter(stage=='Included in analysis') %>% pull(n) %>% sum()
perc.include = round(100*n.include/n.api)
min.perc.stats = total.records[[2]] %>% filter(percentage==min(percentage)) %>% select(volume,percentage)
max.perc.stats = total.records[[2]] %>% filter(percentage==max(percentage)) %>% select(volume,percentage)
```

```{r}
load('../../results/wordcount.plos.rda')
n.words = wordcounts %>% summarise(med = median(words),q1=quantile(words,.25),q3=quantile(words,.75))
p.extremes = wordcounts %>% summarise(morethan500 = round(100*mean(words>500)),lessthan50=round(100*mean(words<50)))
n.extremes = wordcounts %>% summarise(morethan500 = sum(words>500),lessthan50=sum(words<50))
```

```{r, echo=FALSE, fig.align='center', out.width="95%", fig.cap="PLOS ONE result summary."}
knitr::include_graphics("figures/plos.summary.jpg")
```

<!-- ![\label{fig:plos-n}A: Search results by _PLOS ONE_ volume; B: word count per statistical methods section included in analysis (n = 111,73); C: subject classifications assigned to full-text records included in analysis](figures/plos.summary.jpg) -->

```{r,fig.height=12,fig.width=6,fig.asp=0.55,fig.cap='\\label{fig:plos-n}Search results by _PLOS ONE_ volume (1st row); word count per statistical methods section included in analysis (n = 111,731; 2nd row); subject classifications assigned to full-text records included in analysis (3rd row)'}

load('../../results/stats_section_subject.classifications.rda')
stats_section_subject = mutate(stats_section_subject,
                               top3 = ifelse(subject_level_number %in% 1:3,1,0))

@@

```{r, echo=FALSE, fig.align='center', out.width="70%", fig.cap="PLOS ONE topic clouds."}
knitr::include_graphics("figures/plos.wordclouds.jpg")
```

@@

```{r}
load('../../results/plos.results.10topics.rda')

@@

\subsection{ANZCTR}

```{r, echo=FALSE, fig.align='center', out.width="70%", fig.cap="ANZCTR topic clouds."}
knitr::include_graphics("figures/anzctr.wordclouds.jpg")
```

\section{Supplementary}

\subsection{PLOS}

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.cap="PLOS ONE clustering metrics."}
knitr::include_graphics("figures/supplementary/supp_plosone.50clusters.jpg")
```

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.cap="PLOS ONE topic values."}
knitr::include_graphics("figures/supplementary/plos.topicvalues.jpg")
```

\subsection{ANZCTR}

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.cap="ANZCTR clustering metrics."}
knitr::include_graphics("figures/supplementary/supp_anzctr.50clusters.jpg")
```

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.cap="ANZCTR topic values."}
knitr::include_graphics("figures/supplementary/anzctr.topicvalues.jpg")
```

### 2021-04-21 manuscript/asa_template/asa_template.tex
update figures and tex files

\begin{figure}
\centering
\includegraphics{figures/figure1.jpg}
\caption{\label{fig:plos-n}A: Search results by \emph{PLOS ONE} volume;
B: word count per statistical methods section included in analysis (n =
111,73); C: subject classifications assigned to full-text records
included in analysis}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/figure2.jpg}
\caption{\label{fig:plot-10-topics}Topic clouds summarising common terms
in \emph{PLOS ONE} statistical methods sections assuming ten clusters}
\end{figure}

@@

\includegraphics[width=3.75in,height=2.75in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-4-1.png}

@@

>>>>

\begin{figure}

{\centering \includegraphics[width=0.95\linewidth]{figures/plos.summary}

}

\caption{PLOS ONE result summary.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{figures/plos.wordclouds}

}

\caption{PLOS ONE topic clouds.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\includegraphics[width=3.75in,height=2.75in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-6-1.png}

@@

\subsection{ANZCTR}

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{figures/anzctr.wordclouds}

}

\caption{ANZCTR topic clouds.}\label{fig:unnamed-chunk-7}
\end{figure}

\section{Supplementary}

\subsection{PLOS}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{figures/supplementary/supp_plosone.50clusters}

}

\caption{PLOS ONE clustering metrics.}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{figures/supplementary/plos.topicvalues}

}

\caption{PLOS ONE topic values.}\label{fig:unnamed-chunk-9}
\end{figure}

\subsection{ANZCTR}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{figures/supplementary/supp_anzctr.50clusters}

}

\caption{ANZCTR clustering metrics.}\label{fig:unnamed-chunk-10}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{figures/supplementary/anzctr.topicvalues}

}

\caption{ANZCTR topic values.}\label{fig:unnamed-chunk-11}
\end{figure}
